Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-26 paper.tex
update

In the rest of this section, we take a closer look at the P4F which is the
state-of-art techniques to accomplish perfect call-stack precision on small-step
AAMs, and Abstracting De nitional Interpreters (ADI) that adpots another 
approach to pushdown control flow analysis.

@@

%probably Store Widening \& Abstract Garbage Collection
%monadic
\subsection{Monadification: From Refunctionalized AAM to ADI}

@@

\subsection{Un-CPS: From Refunctionalized AAM to Direct Style}

@@

>>>>

In the rest of this section, we take a closer look at the P4F which is the
state-of-art techniques to accomplish perfect call-stack precision on small-step
AAMs, and Abstracting Defnitional Interpreters (ADI) that adpots another 
approach to pushdown control flow analysis.

@@

%probably Store Widening \& Abstract Garbage Collection
%monadic
\subsection{Monadification: to Abstracting Definitional Interpreter}

@@

\subsection{Un-CPS: to Yet Another Abstracting Definitional Interpreter}

@@

TODO: use delimited continuation? 
Another form of abstracting definitional interpreter.
